---
title: "Springboard Titanic Data Wrangling"
output: html_notebook
---

Load Packages & Import Data

```{r}
library("tidyverse")

titanic_data <- read.csv("titanic_original.csv", stringsAsFactors = FALSE)

```

Preview the Data

```{r}
str(titanic_data)

```

1. Port of Embarkation: Missing values correspond to passengers who embarked from Southhampton.

Replace the missing values with "S". 

```{r}
titanic_data <- titanic_data %>% 
  mutate(embarked = if_else(embarked == "", "S" , embarked))

```

2. Age: There are a lot of missing values in the age column. 

Replace the missing values witht the mean age

```{r}
age_missing <- na.omit(titanic_data$age)

mean_age <- round(mean(age_missing), digits = 0)

mean_age
```

Age: Consider other ways to populate the missing values. 

Depending on the distributon, it may make more sense to us the medain. 

Create histogram

```{r}
hist(titanic_data$age)
```

Since the distribtuion is skwed left, the medain should be used instead of the mean. This is beacuse the median is not effected by extreme values, therefore it is a better repersentation of the central tendency.

Replace missing values with medain.

```{r}
median_age <- median(age_missing)

median_age

titanic_data$age[is.na(titanic_data$age)] <- median_age
```

3. Lifeboat: Many passengers did not make to a lifeboat. Fill empty slots with "NA"

```{r}
titanic_data$boat[titanic_data$boat == ""] <- "NA"

```

4. Cabin: Many passengers don't have passengers don't have cabin number associated with them. 

For further analysis we should fill the missing vlaues with a binary dummy values. 

```{r}
titanic_data$cabin[titanic_data$cabin == ""] <- "NA"

cabin_has_number <- ifelse(titanic_data$cabin == "NA", 0, 1)

titanic_data$cabin_has_number <- cabin_has_number
```

5. Write clean csv file: write new csv with the cleaned up data and save it as titanic_clean.csv

```{r}
# view clean data

view(titanic_data)

write.table(titanic_data, "titanic_clean.csv", sep = ",")
```


