---
title: "Springboard Titanic Data Wrangling"
output: html_notebook
---

Load Packages & Import Data

```{r}
library("tidyverse")

titanic_data <- read.csv("titanic_original.csv", stringsAsFactors = FALSE)

```

Preview the Data

```{r}
titanic_data

```

Port of Embarkation: Missing values correspond to passengers who embarked from Southhampton.

Replace the missing values with "S". 

```{r}
titanic_data <- titanic_data %>% 
  mutate(embarked = if_else(embarked == "", "S" , embarked))

```

Age: There are a lot of missing values in the age column. 

Replace the missing values witht the mean age

```{r}
age_missing <- na.omit(titanic_data$age)

mean_age <- round(mean(age_missing), digits = 0)

titanic_data$age[is.na(titanic_data$age)] <- mean_age
```

Age: Consider other ways to populate the missing values. 

Depending on the distributon, it may make more sense to us the medain. 

Create histogram

```{r}
hist(titanic_data$age)
```

Since the distribtuion is skwed left, the medain should be used instead of the mean. This is beacuse the median is not effected by extreme values, therefore it is a better repersentation of the central tendency.

Replace missing values with medain.

```{r}
median_age <- median(age_missing)

```

